Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-11-10 paper/main.tex

A cryptographic hash function is a deterministic mathematical procedure which
takes an arbitrary block of data and outputs a fixed-size bit string. The output
is referred to as the hash value, message digest or simply digest.
Another property of a cryptographic hash function is that the smallest change in
the input data (e.g. one bit) should completely change the output of the hash
function. In other words it should be infeasible to find the reverse of a
cryptographic hash function \cite{stallings}. It should also be infeasible to
find two blocks of data which produce the same hash value (a \emph{collision}).

@@

\paragraph{Security.} The most important criteria for the SHA-3
candidates\cite{s_nistround2} is security. The full description of security
criteria are mentioned in \cite{s_fedreg}, however the most noteworthy criterion
in regards to Tahoe-\ac{LAFS} is that \ac{SHA}-3 candidates are required to have
resistance against length-extension attacks. Both \ac{SHA}-1 and the \ac{SHA}-2
family are vulnerable to this attack\cite{s_mdre}, and this requires Tahoe to
run the algorithm twice, as described by .
%TODO: cite Practical cryptography/Niels Ferguson, Bruce Schneier

@@

\paragraph{Algorithm and implementation characteristics.} By this 3rd criteria,
\ac{NIST} emphasis that algorithms with greater flexibility will be given
preference over other algorithms \cite{s_nistround2}. By flexible they imply the
possibility of the function to run efficiently on a variety of platforms, and to
use parallelism or instruction set extensions. Another key point of a flexible
hash function is that it should have a simple and elegant design to encourage
understanding, analysis and design confidence.

@@

The Round 2 \ac{SHA}-3 candidates are all included in the toolkit, with a number
of different optimizations for each candidate. Optimizations range from
32-/64-bit specific implementations, the use of extended instruction sets such
as \ac{SSE2} and \ac{SSSE3}, optimizations for different number of cores and
others. The toolkit will also try different compiler optimizations to get the
best results possible for each function.
% TODO: Insert image to visualize the forest of different implementations.

>>>>

A cryptographic hash function is a deterministic mathematical procedure which
takes an arbitrary block of data and outputs a fixed-size bit string. The output
is referred to as the hash value, message digest or simply digest.
Another property of a cryptographic hash function is that the smallest change in
the input data (e.g. one bit) should completely change the output of the hash
function. In other words it should be infeasible to find the reverse of a
cryptographic hash function \cite[p. 335]{stallings}. It should also be infeasible to
find two blocks of data which produce the same hash value (a \emph{collision}).

@@

\paragraph{Security.} The most important criteria for the SHA-3
candidates\cite{s_nistround2} is security. The full description of security
criteria are mentioned in \cite{s_fedreg}, however the most noteworthy criterion
in regards to Tahoe-\ac{LAFS} is that \ac{SHA}-3 candidates are required to have
resistance against length-extension attacks. Both \ac{SHA}-1 and the \ac{SHA}-2
family are vulnerable to this kind of attack, and thus requires
Tahoe to run the algorithm twice, as described by \citet{schneier}.

@@

\paragraph{Algorithm and implementation characteristics.} By this 3rd criteria,
\ac{NIST} emphasizes that algorithms with greater flexibility will be given
preference over other algorithms \cite{s_nistround2}. By flexible, they imply
the possibility of the function to run efficiently on a variety of platforms,
and to use parallelism and instruction set extensions. Another key point of a
flexible hash function is that it should have a simple and elegant design to
encourage understanding, analysis and design confidence.

@@

The Round 2 \ac{SHA}-3 candidates are all included in the toolkit, with a number
of different optimizations for each candidate. Optimizations range from
32-/64-bit specific implementations, the use of extended instruction sets such
as \ac{SSE2} and \ac{SSE3}, optimizations for different number of cores and
others. The toolkit will also try different compiler optimizations to get the
best results possible for each function.
% TODO: Insert image to visualize the forest of different implementations.
